### 2016-09-29 results.tex
GBF

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\dbinom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
%\input{Theorem3_FP}

@@

In~\cite{xxx} the GBF is a central piece of a private set-intersection
scheme

The authors note that the GBF is of general interest, so we consider
its correctness and

The pseudocode captures
two version, one in which the

If the filter and the hash functions are public, there is a naive
attack that works for some interesting parameters.  Pick~$k$ positions
$i_1,i_2,\ldots,i_k$, xor strings at these positions to get a
candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots
\wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a
false-positive. (You don't have to do all~$k$ hashes, you can stop as
soon as one fails to match the index.) Say you have a 1000-position
filter ($m=1000$) and a 100-element set ($n=100$), and you are willing
to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There
are roughly $2^{35}$ subsets of 4 indices to consider, which is
reasonable on a laptop these days.  (Also, since $n=100$ the expected
number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you
find a winner then almost certainly it is in the set.  Granted, this
attack is naive, but notice that you \emph{cannot} mount it against a
standard Bloom filter. Also notice that this attack might be
significantly more efficient than brute force guessing over the
universe of inputs (imagine that $U=\bits^{64}$), even if you know
that the distribution deviates significantly from uniform.

>>>>

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
of moving from the adaptive to the zero-query setting.
Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
which case the final term in the bound behaves as
$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$(q_T+q_H)$ attempts.
%\input{Theorem3_FP}

@@

In~\cite{xxx} the GBF is a central piece of a private set-intersection
scheme, in which the client computes a classical BF over its
set~$S_1$, the server computes a GBF over its set~$S_2$, and then an
oblivious transfer protocol is carried out, at the end of which the
client obtains a GBF for $S_1 \cap S_2$ (the server learns nothing).
The authors note that the GBF is a new set-membership data strucure
that may be of general interest, so we explore its correctness and
privacy with respect to use case that may or may not make the
representation~$M$ public. The pseudocode in Figure~\ref{fig:gbf}
covers both possibilities.

We note that~\cite{xxx} provides error-rate analysis, i.e., the
probability of finding a single false-positive in a non-adaptive
attack.  When $\lambda$ is the bit-length of the xor-shares, they
argue that the error-rate is at most $2^{-\lambda}$, roughly because
the xor-shares stored in~$M$ are random strings.  (Note that
  this is independent of~$k,m,n$; although $k>1$ is required for the
  xor shares.)  However, this analysis implicilty assumes that the potential false-positive string~$x$ is fixed
\emph{before}~$M$ is determined.  We will see that this carries over
\tsnote{I think?} to the case in which~$M$ is private (i.e.,
$\pubaux=\emptystring,\privaux=\langle M \rangle$), but when~$M$ is
public things are different.

Consider the adversary described in Figure~\ref{fig:adv-gbf}.  In one
round of the for-loop, it pics~$k$ positions $i_1,i_2,\ldots,i_k$, and
xors the strings at these positions to get a candidate~$x$.   If $x
\in S$, which the adversary knows in the correctness experiment, then
it moves on to a new set of positions.  If $x \not\in S$ and 
$h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$,
then it \emph{must be} that $x$ is a false-positive.   Indeed, note
that the probability of this (in the ROM) is precisely the
false-positive rate of a classical BF using the same $(k,m,n)$ as the GBF.

Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
set-membership query would be laughable in many applications, and a
$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
that, as described in~\cite{xxx}, $\lambda$ must be at least the
bitlength of the longest element $x \in S$. \tsnote{This could be
  handled with a slight change to the set membership test, by checking
if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
of~$x$.}}
Let us consider a practically interesting set of parameters. Say you have a 1000-position
filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
functions (a la Squid\cite{squid}).  This results in a false-positive rate of
approximately 1\% in a classical BF.  There are roughly $2^{35}$
subsets of four indices to consider, which is reasonable on a laptop
these days.  Moreover, with $n=100$ the expected
number of trials is roughly $2^{28}$.   
Note that the attack is easily extended to find $r>1$ false positives.

We admit that attack is not particularly sophisticated, yet it might
be significantly more efficient than brute force guessing over the
universe of inputs (imagine that $\elts=\bits^{128}$), even if you know
that the distribution deviates significantly from uniform. Notice,
too, that you \emph{cannot} mount it against a standard Bloom
filter.

\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
\begin{theorem}
Fix $k,m,n,r,\lambda>0$, a set~$\elts$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the garbled Bloom filter (set membership) data structure over~$\elts$. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}
